Federated Learning's Blessing:\\ FedAvg has Linear Speedup

### 2020-06-01 source/sec_intro.tex
Update on Overleaf.

>>>>

\subsection{Related Work}
\textbf{The Convergence of FedAvg and Linear Speedup.}
There has been a vast amount of convergence analysis for FedAvg in different settings. However, most of the prior works provide the
convergence guarantee under a simplified setting, where either statistical
heterogeneity~\cite{stich2018local,zhou2017convergence,wang2018cooperative,woodworth2018graph} or system
heterogeneity~\cite{yu2019parallel,wang2019adaptive,khaled2019first,jiang2018linear} are not
considered. This simplified setting is also referred as local SGD. 
In~\cite{li2019convergence},
the authors for the first time provide convergence of FedAvg for strongly convex problem considering both statistical heterogeneity and system heterogeneity, yet it
didn't achieve linear speedup. In~\cite{haddadpour2019convergence,liang2019variance,huo2020faster,jiang2018linear}, the convergence of FedAvg for non-convex problems has been studied. 
However, \cite{huo2020faster} did not discuss the linear speedup and the theorems in \cite{haddadpour2019convergence,liang2019variance} failed to cover the accelerated version of
FedAvg.

\textbf{Federated Learning Beyond Local SGD.}
% The accelerated SGD methods has achieved optimal convergence rate in strongly convex
% optimization~\cite{nesterov1983method}.
In \cite{liu2019accelerating}, the authors provide a convergence rate of accelerated FedAvg for strongly convex problems, while it is considered in full participation setting.
\cite{yu2019linear} and \citep{huo2020faster} provide
convergence guarantee for Nesterov accelerated FedAvg for non-convex. 
However, \cite{yu2019linear} did not consider the system heterogeneity and \cite{huo2020faster} haven't discuss the linear speedup.
Furthermore, the accelerated FedAvg admitting a similar convergence rate as FedAvg in all previous works.  In this work, we provide a novel accelerated FedAvg with improved convergence rates under a popular overparameterized setting.
